Reasoning About a Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management\\ Technical Appendix Including Proofs and Details

### 2018-02-20 local-capability-machine/local-capability-machine.tex
typo

\newcommand{\isdef}{\mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\tiny\sffamily def}}}{=}}}
\newcommand\bnfdef{\mathrel{::=}}
\title{Reasoning about a Capability Machine with Local Capabilities\\
 Provably Safe Stack and Return Pointer Management (without OS Support)\\
 Technical Appendix Including Proofs and Details}

@@

\section{Logical Relation}
\subsection{Worlds}
Assume a sufficiently large set of states $\States$ that at least contains the states used in this document.
\begin{definition}
  \[
   \Rels = \{\phi_\pub \times \phi \in \powerset{\States^2}\times \powerset{\States^2} \mid \phi_\pub, \phi \text{ is reflexive and transitive and } \phi_\pub \subseteq \phi \}
  \]
\end{definition}

>>>>

\newcommand{\isdef}{\mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\tiny\sffamily def}}}{=}}}
\newcommand\bnfdef{\mathrel{::=}}
\title{Reasoning About a Machine with Local Capabilities\\
 Provably Safe Stack and Return Pointer Management\\
Technical Appendix Including Proofs and Details}

\author{Lau Skorstengaard\\Aarhus University\\\texttt{lask@cs.au.dk}
        \and 
        Dominique Devriese\\imec-DistriNet, KU Leuven\\\texttt{dominique.devriese@cs.kuleuven.be}
        \and 
        Lars Birkedal\\Aarhus University\\\texttt{birkedal@cs.au.dk}}

@@

\section{Logical Relation}
\subsection{Worlds}
Assume a sufficiently large set of states $\States$ that at least contains the states used in this document.
\begin{definition}
  \[
   \Rels = \{(\phi_\pub, \phi) \in \powerset{\States^2}\times \powerset{\States^2} \mid \phi_\pub, \phi \text{ is reflexive and transitive and } \phi_\pub \subseteq \phi \}
  \]
\end{definition}
